---
title: "Lab 00 - Hello IDS!"
author: "Katya Cheltsova"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Kayleigh Innes", "Aimee Tumblety", "Felix Ainsley", 
           "Freddie Elson", "Katya Cheltsova"),
  github_username = c("Kayleighinnes", "aimeet05", "fjainsley", 
                      "freddoderfisch", "katya-c"), 
  colour = c("green", "blue", "purple", 
             "orange", "lavender"),
  hobby = c("film", "guitar", "table tennis", 
            "gym", "piano"),
  favourite_number = c(69, 7, 13, 4, 4)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


The plot shows a bar chart of the team's favorite numbers.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "github_username", 
          y = "favourite_number",
          title = "Team's Favourite Numbers")
```

The 'labs()' command adds axis labels and titles to the graph.

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

Bar chart isn't very good at portraying the data as everyone had different hobbies, so if the was recreated for a larger group of people there would be many different bars showing the same value, a table would better show the data.
